---
title: "Study of MSF methods"
author: "Catarina Wor"
affiliation: "DFO"
abstract:
thanks:
keywords:
date: \today
output:
  pdf_document:
    highlight: default
    citation_package:
    keep_tex: false
    fig_caption: true
    latex_engine: pdflatex
fontsize: 11pt
geometry: margin=1in
bibliography: msfstudy.bib
biblio-style:
header-includes:
- \usepackage{geometry}
- \usepackage{fancyhdr} 
- \usepackage{indentfirst}
- \usepackage{graphicx}
- \usepackage{subfigure}
- \usepackage{amsmath}
- \usepackage{listings}
- \usepackage{tikz}
- \usetikzlibrary{matrix}
---

\vspace{0.25in}



# Overview

This document produces an overview of a set of candidate methods to account for mark-selective fisheries (MSF) in the calculations of calendar year exploitation rates (CYER) for the Chinook Technical Committee (CTC) indicator stocks. 

The methods are divided into two major categories: single index tag (SIT) and double index tag (DIT) methods. 

The list of methods studied in this documet are shown below:
 -  SIT 1: $\lambda_{a}$ is estimating at spawning by age
 -  SIT 2: $\lambda_{a}$ is estimating at spawning by age  updated after successive fisheries
 -  SIT 3: $\lambda$ is estimated at release
 -  SIT 4: $\lambda$ is estimated at release and updated after successive fisheries
 -  SIT 5: $\lambda$ estimated from total exploitation rate and escapement and updated after successive fisheries 

  
# Global inputs


The global inputa for the simulatios shown in this study is based on a sigle year of data and daat is simulated without any observation or process error. The Simulated data produces based on the `create_example_input()` and the `simpop()` mimics the data produced on the 'MSF Methods Beta' excel spreadsheet. 

```{r tidy = TRUE, message = FALSE, warning = FALSE, error = FALSE, include = FALSE}
library("msfmethods")
mydata <- create_example_input()
example_dat <- simpop(mydata) 

```

# SIT 1 

The first single index tagging method assumes that the ratio between unmarked and marked recoveries can only be updated at the escapement level. 

- Assume discard mortality scalar is known
- Assume catch is known without error
- Assume Mark-Selective Fishery Release Mortality Rate is known

```{r tidy = TRUE, message = FALSE, warning = FALSE, error = FALSE, include = FALSE}

example_sit1 <- sit1(example_dat)


#example_sit1$estimated$hre
#example_sit1$data$hru


```

# SIT 2 

The second single index tagging method assumes that the ratio between unmarked and marked recoveries can only be updated at the escapement level and after each terminal fisheries.  

- Assume discard mortality scalar is known
- Assume catch is known without error
- Assume Mark-Selective Fishery Release Mortality Rate is known


```{r tidy = TRUE, message = FALSE, warning = FALSE, error = FALSE, include = FALSE}

example_sit2 <- sit2(example_dat) 

#example_sit2$estimated$hre
#example_sit2$data$hru


```

## SIT 3

## SIT 4

## SIT 5